Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-22 manuscript/response_to_reviews.Rmd

Comments to the Author

This is a resubmission of a previously revised manuscript. I have enjoyed reading the manuscript. The paper is well written and the methods are clearly presented. The hypotheses are sound and well framed within the physiological implications of tree height.

The authors have satisfactorily answered most previous comments. For instance, I appreciated the discussion on the two indices Rt and Rtarima. I agree that results comparing them are pretty similar (Table S6 vs Table S7) and that authors can use Rt.

**Thank you. Because we had to cut content in order to present the recovery and resilience metrics (see below) while keeping within word limits, we have cut back on the reporting of $Rt_{ARIMA}$ results in the main text, but still show the full comparisons in the Appendix. Specifically, we now state in the following in the methods: "$Rt$ and $Rt_{ARIMA}$ were strongly correlated (Fig. **S5**), and showed similar responses to the independent variables of interest (cf. Tables S4-55, S8-S9). Visual review of the individual tree-ring sequences with the largest discrepancies between these metrics revealed that $Rt$ was less prone to unreasonable estimates than $Rt_{ARIMA}$. We therefore determined that use of 5-year means, as described above, were more appropriate metrics than those based on ARIMA projections." We then drop presentation of $Rt_{ARIMA}$ results in the results section.**

@@

* **in the introduction, where we define resistance: "Here, we examine how tree height, microenvironment characteristics, and species' traits collectively shape drought resistance, defined as the ratio of annual stem growth in a drought year to that which would be expected in the absence of drought based on previous years' growth."**

* **in the sentence identified above: "These findings advance our knowledge of the factors that make trees vulnerable to stem growth declines during drought and, by extension, likely make them more vulnerable to mortality [@sapes_plant_2019]."**

Line 385 vs lines 308-309 and line 338: does that mean that there was a correlation between canopy position and positive Rt? Can it also be related to moisture sensitivity of different species, or to niche (microenvironment) partitioning among species? (as nicely discussed in lines 420-422). I see from lines 445-450 that sampled FAGR were small, which is coherent with the authors’ statement.

**Yes, although we do not include canopy position in our statistical models. To make the link between high $Rt$ and increased growth, we have modified the sentence previously on line 385 to read, "Across all three droughts, the majority of trees experienced reduced growth, but a substantial portion (e.g., short understory trees, species with drought resistant traits*) had increased growth (Figs. **1b, 4**), consistent with prior observations that smaller trees can exhibit increased growth rates during drought [@bennett_larger_2015]."**

### 2020-09-22 manuscript/climate_sensitivity_draft.Rmd
Ryan's fixes
we're missing a few citations. I created Exported Items.bib with the refs, but for some reason its breaking the system when I add them to book.bib. That needs to be figured out.

In contrast, *hydraulic traits have direct physiological linkages to tree growth and mortality responses to drought. 
For instance, water potentials at which percent the loss of conductivity surpasses a certain threshold (e.g., P50 and P88, representing 50 and 88% loss of conductivity, respectively) and hydraulic safety margin (*i.e.*, difference between typical minimum water potentials and P50 or P88) correlate with drought performance across global forests [@anderegg_meta-analysis_2016]. 
However, these are time-consuming to measure and therefore infeasible for predicting or modeling drought responses in highly diverse forests (*e.g.*, in the tropics).
More easily-measurable* leaf drought tolerance traits that have direct linkage to plant hydraulic function can explain variation in plant distribution and function [@medeiros_extensive_2019]. 
These include leaf area shrinkage upon desiccation [$PLA_{dry}$; @scoffoni_leaf_2014] and the leaf water potential at turgor loss point ($\pi_{tlp}$), *i.e.,* the water potential at which leaf wilting occurs [@bartlett_correlations_2016; @zhu_leaf_2018]. 
Both traits correlate with hydraulic vulnerability and drought tolerance as part of unified plant hydraulic systems [@scoffoni_leaf_2014; @bartlett_correlations_2016; @zhu_leaf_2018; @farrell_does_2017].
The abilities of both $PLA_{dry}$ and $\pi_{tlp}$ to explain the drought tolerance of tree growth remains untested [but see @powers_catastrophic_2020 for $\pi_{tlp}$ link to mortality].

>>>>

In contrast, hydraulic traits have direct physiological linkages to tree growth and mortality responses to drought. 
For instance, water potentials at which percent the loss of conductivity surpasses a certain threshold (e.g., P50 and P88, representing 50 and 88% loss of conductivity, respectively) and hydraulic safety margin (*i.e.*, difference between typical minimum water potentials and P50 or P88) correlate with drought performance across global forests [@anderegg_meta-analysis_2016]. 
However, these are time-consuming to measure and therefore infeasible for predicting or modeling drought responses in highly diverse forests (*e.g.*, in the tropics).
More easily-measurable leaf drought tolerance traits that have direct linkage to plant hydraulic function can explain variation in plant distribution and function [@medeiros_extensive_2019]. 
These include leaf area shrinkage upon desiccation [$PLA_{dry}$; @scoffoni_leaf_2014] and the leaf water potential at turgor loss point ($\pi_{tlp}$), *i.e.,* the water potential at which leaf wilting occurs [@bartlett_correlations_2016; @zhu_leaf_2018]. 
Both traits correlate with hydraulic vulnerability and drought tolerance as part of unified plant hydraulic systems [@scoffoni_leaf_2014; @bartlett_correlations_2016; @zhu_leaf_2018; @farrell_does_2017].
The abilities of both $PLA_{dry}$ and $\pi_{tlp}$ to explain the drought tolerance of tree growth remains untested [but see @powers_catastrophic_2020 for $\pi_{tlp}$ link to mortality].
